\section{Grammaire des PCRE en langage PP}
\label{appendices:grammar_of_pcre}

Dans la partie~\ref{subsection:data:pp}, nous précisons que les lexèmes des
grammaires sont exprimés avec des expressions régulières. Ces dernières
utilisent le vocabulaire des PCRE~\acite{Hazel05}. Dans
partie~\ref{subsection:data:isotropic_generation}, lorsque nous expliquons
comment une séquence de lexèmes est concrétisée vers une chaîne de caractère,
nous expliquons que nous utilisons la grammaire des PCRE pour obtenir un AST
(\inenglish{Abstract Syntax Tree}) après analyse de chaque lexème. Cet AST est
visité pour appliquer un algorithme de génération aléatoire isotropique. Cette
partie présente la grammaire des PCRE au format PP. La dernière version de la
grammaire est disponible à l'adresse~:
\url{http://central.hoa-project.net/Resource/Library/Regex/Grammar.pp}.

\begin{bigbigpre}
// \\
// Hoa \\
// \\
// \\
// @license \\
// \\
// New BSD License \\
// \\
// Copyright © 2007-2014, Ivan Enderlin. All rights reserved. \\
// \\
// Redistribution and use in source and binary forms, with or without \\
// modification, are permitted provided that the following conditions are met: \\
//     * Redistributions of source code must retain the above copyright \\
//       notice, this list of conditions and the following disclaimer. \\
//     * Redistributions in binary form must reproduce the above copyright \\
//       notice, this list of conditions and the following disclaimer in the \\
//       documentation and/or other materials provided with the distribution. \\
//     * Neither the name of the Hoa nor the names of its contributors may be \\
//       used to endorse or promote products derived from this software without \\
//       specific prior written permission. \\
// \\
// THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" \\
// AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE \\
// IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE \\
// ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDERS AND CONTRIBUTORS BE \\
// LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR \\
// CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF \\
// SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS \\
// INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN \\
// CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) \\
// ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE \\
// POSSIBILITY OF SUCH DAMAGE. \\
// \\
// Grammar \bslash{}Hoa\bslash{}Regex\bslash{}Grammar. \\
// \\
// Provide grammar of PCRE (Perl Compatible Regular Expression)for the LL(k) \\
// parser. More informations at http://pcre.org/pcre.txt, sections pcrepattern & \\
// pcresyntax. \\
// \\
// @author     Ivan Enderlin <ivan.enderlin@hoa-project.net> \\
// @copyright  Copyright © 2007-2014 Ivan Enderlin. \\
// @license    New BSD License \\
// \\
 \\
 \\
// Skip. \\
%skip   nl                       \bslash{}n \\
 \\
// Character classes. \\
%token  negative_class_          \bslash{}[\bslash{}^ \\
%token  class_                   \bslash{}[ \\
%token _class                    \bslash{}] \\
%token  range                    \bslash{}- \\
 \\
// Lookahead and lookbehind assertions. \\
%token  lookahead_               \bslash{}(\bslash{}?= \\
%token  negative_lookahead_      \bslash{}(\bslash{}?! \\
%token  lookbehind_              \bslash{}(\bslash{}?<= \\
%token  negative_lookbehind_     \bslash{}(\bslash{}?<! \\
 \\
// Conditions. \\
%token  named_reference_         \bslash{}(\bslash{}?\bslash{}(<            -> nc \\
%token  absolute_reference_      \bslash{}(\bslash{}?\bslash{}((?=\bslash{}d)       -> c \\
%token  relative_reference_      \bslash{}(\bslash{}?\bslash{}((?=[\bslash{}+\bslash{}-])   -> c \\
%token  c:index                  [\bslash{}+\bslash{}-]?\bslash{}d+         -> default \\
%token  assertion_reference_     \bslash{}(\bslash{}?\bslash{}( \\
 \\
// Comments. \\
%token  comment_                 \bslash{}(\bslash{}?#              -> co \\
%token  co:_comment              \bslash{})                 -> default \\
%token  co:comment               .*?(?=(?<!\bslash{}\bslash{})\bslash{})) \\
 \\
// Capturing group. \\
%token  named_capturing_         \bslash{}(\bslash{}?<              -> nc \\
%token  nc:_named_capturing      >                  -> default \\
%token  nc:capturing_name        .+?(?=(?<!\bslash{}\bslash{})>) \\
%token  non_capturing_           \bslash{}(\bslash{}?: \\
%token  non_capturing_reset_     \bslash{}(\bslash{}?\bslash{}| \\
%token  atomic_group_            \bslash{}(\bslash{}?> \\
%token  capturing_               \bslash{}( \\
%token _capturing                \bslash{}) \\
 \\
// Quantifiers (by default, greedy). \\
%token  zero_or_one_possessive   \bslash{}?\bslash{}+ \\
%token  zero_or_one_lazy         \bslash{}?\bslash{}? \\
%token  zero_or_one              \bslash{}? \\
%token  zero_or_more_possessive  \bslash{}*\bslash{}+ \\
%token  zero_or_more_lazy        \bslash{}*\bslash{}? \\
%token  zero_or_more             \bslash{}* \\
%token  one_or_more_possessive   \bslash{}+\bslash{}+ \\
%token  one_or_more_lazy         \bslash{}+\bslash{}? \\
%token  one_or_more              \bslash{}+ \\
%token  exactly_n                \bslash{}\{[0-9]+\bslash{}\} \\
%token  n_to_m_possessive        \bslash{}\{[0-9]+,[0-9]+\bslash{}\}\bslash{}+ \\
%token  n_to_m_lazy              \bslash{}\{[0-9]+,[0-9]+\bslash{}\}\bslash{}? \\
%token  n_to_m                   \bslash{}\{[0-9]+,[0-9]+\bslash{}\} \\
%token  n_or_more_possessive     \bslash{}\{[0-9]+,\bslash{}\}\bslash{}+ \\
%token  n_or_more_lazy           \bslash{}\{[0-9]+,\bslash{}\}\bslash{}? \\
%token  n_or_more                \bslash{}\{[0-9]+,\bslash{}\} \\
 \\
// Alternation. \\
%token alternation               \bslash{}| \\
 \\
// Literal. \\
%token character                 \bslash{}\bslash{}([aefnrt]|c[\bslash{}x00-\bslash{}x7f]) \\
%token dynamic_character         \bslash{}\bslash{}([0-7]\{3\}|x[0-9a-zA-Z]\{2\}|x\{[0-9a-zA-Z]+\}) \\
// Please, see PCRESYNTAX(3), General Category properties, PCRE special category \\
// properties and script names for \bslash{}p\{\} and \bslash{}P\{\}. \\
%token character_type            \bslash{}\bslash{}([CdDhHNRsSvVwWX]|[pP]\{[^\}]+\}) \\
%token anchor                    \bslash{}\bslash{}(bBAZzG)|\bslash{}^|\bslash{}$ \\
%token match_point_reset         \bslash{}\bslash{}K \\
%token literal                   \bslash{}\bslash{}.|. \\
 \\
 \\
// Rules. \\
 \\
#expression: \\
    alternation() \\
 \\
alternation: \\
    concatenation() ( ::alternation:: concatenation() #alternation )* \\
 \\
concatenation: \\
    (   assertion() | quantification() | condition() ) \\
    ( ( assertion() | quantification() | condition() ) #concatenation )* \\
 \\
#condition: \\
    ( \\
        ::named_reference_:: <capturing_name> ::_named_capturing:: #namedcondition \\
      | ( \\
            ::relative_reference_:: #relativecondition \\
          | ::absolute_reference_:: #absolutecondition \\
        ) \\
        <index> \\
      | ::assertion_reference_:: alternation() #assertioncondition \\
    ) \\
    ::_capturing:: concatenation()? \\
    ( ::alternation:: concatenation()? )? \\
    ::_capturing:: \\
 \\
assertion: \\
    ( \\
        ::lookahead_::           #lookahead \\
      | ::negative_lookahead_::  #negativelookahead \\
      | ::lookbehind_::          #lookbehind \\
      | ::negative_lookbehind_:: #negativelookbehind \\
    ) \\
    alternation() ::_capturing:: \\
 \\
quantification: \\
    ( class() | simple() ) ( quantifier() #quantification )? \\
 \\
quantifier: \\
    <zero_or_one_possessive>  | <zero_or_one_lazy>  | <zero_or_one> \\
  | <zero_or_more_possessive> | <zero_or_more_lazy> | <zero_or_more> \\
  | <one_or_more_possessive>  | <one_or_more_lazy>  | <one_or_more> \\
  | <exactly_n> \\
  | <n_to_m_possessive>       | <n_to_m_lazy>       | <n_to_m> \\
  | <n_or_more_possessive>    | <n_or_more_lazy>    | <n_or_more> \\
 \\
#class: \\
    ( \\
        ::negative_class_:: #negativeclass \\
      | ::class_:: \\
    ) \\
    ( range() | literal() )+ \\
    ::_class:: \\
 \\
#range: \\
    literal() ::range:: literal() \\
 \\
simple: \\
    capturing() \\
  | literal() \\
 \\
capturing: \\
    ::comment_:: <comment>? ::_comment:: #comment \\
  | ( \\
        ::named_capturing_:: <capturing_name> ::_named_capturing:: #namedcapturing \\
      | ::non_capturing_:: #noncapturing \\
      | ::non_capturing_reset_:: #noncapturingreset \\
      | ::atomic_group_:: #atomicgroup \\
      | ::capturing_:: \\
    ) \\
    alternation() ::_capturing:: \\
 \\
literal: \\
    <character> \\
  | <dynamic_character> \\
  | <character_type> \\
  | <anchor> \\
  | <match_point_reset> \\
  | <literal>
\end{bigbigpre}
