\section{Grammaire du langage PP en langage PP}
\label{appendices:grammar_of_pp}

\begin{bigbigpre}
// \\
// Hoa \\
// \\
// \\
// @license \\
// \\
// New BSD License \\
// \\
// Copyright © 2007-2014, Ivan Enderlin. All rights reserved. \\
// \\
// Redistribution and use in source and binary forms, with or without \\
// modification, are permitted provided that the following conditions are met: \\
//     * Redistributions of source code must retain the above copyright \\
//       notice, this list of conditions and the following disclaimer. \\
//     * Redistributions in binary form must reproduce the above copyright \\
//       notice, this list of conditions and the following disclaimer in the \\
//       documentation and/or other materials provided with the distribution. \\
//     * Neither the name of the Hoa nor the names of its contributors may be \\
//       used to endorse or promote products derived from this software without \\
//       specific prior written permission. \\
// \\
// THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" \\
// AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE \\
// IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE \\
// ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDERS AND CONTRIBUTORS BE \\
// LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR \\
// CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF \\
// SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS \\
// INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN \\
// CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) \\
// ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE \\
// POSSIBILITY OF SUCH DAMAGE. \\
// \\
// Grammar \bslash{}Hoa\bslash{}Compiler\bslash{}Llk. \\
// \\
// Provide grammar for the LL(k) parser. \\
// \\
// @author     Ivan Enderlin <ivan.enderlin@hoa-project.net> \\
// @copyright  Copyright © 2007-2014 Ivan Enderlin. \\
// @license    New BSD License \\
// \\
 \\
 \\
%skip   space          \bslash{}s \\
 \\
%token  or             \bslash{}| \\
%token  zero_or_one    \bslash{}? \\
%token  one_or_more    \bslash{}+ \\
%token  zero_or_more   \bslash{}* \\
%token  n_to_m         \bslash{}{[0-9]+,[0-9]+\bslash{}} \\
%token  zero_to_m      \bslash{}{,[0-9]+\bslash{}} \\
%token  n_or_more      \bslash{}{[0-9]+,\bslash{}} \\
%token  exactly_n      \bslash{}{[0-9]+\bslash{}} \\
 \\
%token  token          [a-zA-Z_][a-zA-Z0-9_]* \\
 \\
%token  skipped        :: \\
%token  kept_          < \\
%token _kept           > \\
%token  named          \bslash{}(\bslash{}) \\
%token  node           #[a-zA-Z][a-zA-Z0-9]+ \\
 \\
%token  capturing_     \bslash{}( \\
%token _capturing      \bslash{}) \\
%token  unification_   \bslash{}[ \\
%token  unification    [0-9]+ \\
%token _unification    \bslash{}] \\
 \\
#rule: \\
    choice() \\
 \\
choice: \\
    concatenation() ( ::or:: concatenation() #choice )* \\
 \\
concatenation: \\
    repetition() ( repetition() #concatenation )* \\
 \\
repetition: \\
    simple() ( quantifier() #repetition )? <node>? \\
 \\
simple: \\
    ::capturing_:: choice() ::_capturing:: \\
  | ::skipped:: <token> ( ::unification_:: <unification> ::_unification:: )? \\
    ::skipped:: #skipped \\
  | ::kept_:: <token> ( ::unification_:: <unification> ::_unification:: )? \\
    ::_kept:: #kept \\
  | <token> ::named:: \\
    ( ::unification_:: <unification> ::_unification:: )? #named \\
 \\
quantifier: \\
    <zero_or_one> \\
  | <one_or_more> \\
  | <zero_or_more> \\
  | <n_to_m> \\
  | <n_or_more> \\
  | <exactly_n>
\end{bigbigpre}
